{{< include /_setup.qmd >}}

# Synopsis

```{r}
#| label: synopsis

synopsis <- tibble::tribble(
  ~Item, ~Detail,
  "Protocol number", "NVT-AD-3001",
  "Study title", "A 24-week, randomised, double-blind, placebo-controlled study of xanomeline transdermal therapeutic system in patients with mild to moderate Alzheimer's disease",
  "Sponsor", "Nordvale Therapeutics",
  "Investigational product", "Xanomeline transdermal therapeutic system (TTS)",
  "Study phase", "Phase 2",
  "Indication", "Mild to moderate Alzheimer's disease",
  "Study design", "Randomised, double-blind, placebo-controlled, three parallel groups",
  "Treatment groups", "Placebo, xanomeline low dose (50 cm2), xanomeline high dose (75 cm2)",
  "Planned duration of treatment", "24 weeks",
  "Primary endpoint", "Time to first dermatologic treatment-emergent adverse event",
  "Secondary endpoint", "Change from baseline in systolic blood pressure at week 24",
  "Analysis populations", "Randomised population and safety population",
  "Statistical methods", "Kaplan-Meier estimation and Cox proportional hazards for the primary endpoint; analysis of covariance for the secondary endpoint"
)

gt_nordvale(synopsis) |>
  gt::cols_label(Item = "", Detail = "") |>
  gt::cols_width(Item ~ gt::pct(28), Detail ~ gt::pct(72)) |>
  gt::tab_style(
    style = gt::cell_text(weight = "bold"),
    locations = gt::cells_body(columns = "Item")
  )
```

## Subject disposition and key results

```{r}
#| label: synopsis-numbers

randomised <- nrow(adsl)
treated <- sum(adsl[["SAFFL"]] == "Y")
completed <- sum(adsl[["COMPFL"]] == "Y")
with_teae <- dplyr::n_distinct(adae[["USUBJID"]])
with_derm <- dplyr::n_distinct(dplyr::filter(adae, DERMFL == "Y")[["USUBJID"]])
```

A total of `r randomised` subjects were randomised and `r treated` received at least one dose of study drug.
Of these, `r completed` subjects (`r sprintf("%.1f%%", 100 * completed / treated)`) completed the 24-week treatment period.

At least one treatment-emergent adverse event was reported for `r with_teae` subjects (`r sprintf("%.1f%%", 100 * with_teae / treated)`), and `r with_derm` subjects (`r sprintf("%.1f%%", 100 * with_derm / treated)`) reported at least one dermatologic treatment-emergent adverse event.
Dermatologic events occurred earlier and more frequently in both xanomeline groups than in the placebo group, which is consistent with the transdermal route of administration.

No new safety signal was identified beyond the application-site and dermatologic events expected for this formulation.
