{{< include /_setup.qmd >}}

# Study patients

## Analysis populations

::: {#tbl-populations}

```{r}
#| label: populations

tlf_output(tlf_populations(adsl), "populations")
```

`{r} tlf_caption("populations")`

:::

Every randomised subject received at least one dose of study drug, so the randomised, intention-to-treat and safety populations contain the same subjects.
They are not interchangeable in the tables that follow: population tables and efficacy analyses count subjects under the treatment to which they were randomised, whereas safety analyses count them under the treatment actually received, and `r sum(as.character(adsl[["TRT01P"]]) != as.character(adsl[["TRT01A"]]))` subjects randomised to the high dose received the low dose instead.

## Disposition of subjects

::: {#tbl-disposition}

```{r}
#| label: disposition

tlf_output(tlf_disposition(adsl), "disposition")
```

`{r} tlf_caption("disposition")`

:::

```{r}
#| label: disposition-numbers

discontinued <- sum(adsl[["COMPFL"]] == "N")
deaths <- sum(!is.na(adsl[["DTHFL"]]) & adsl[["DTHFL"]] == "Y")
reasons <- sort(table(adsl[["DCSREAS"]]), decreasing = TRUE)
leading_reason <- tolower(names(reasons)[[1L]])
```

`r discontinued` subjects discontinued the study before the end of the treatment period, and `r deaths` deaths were reported.
The most frequent reason for discontinuation was `r leading_reason`, recorded for `r reasons[[1L]]` of the `r discontinued` subjects who discontinued, and discontinuation was more frequent in the xanomeline groups than in the placebo group.

## Protocol deviations

The pilot study underlying this demonstration ships no protocol deviation dataset, so deviations can be reported only where they ended a subject's participation.
`r sum(!is.na(adsl[["DCSREAS"]]) & adsl[["DCSREAS"]] == "Protocol violation")` subjects discontinued for a protocol violation; they are listed in @lst-deviation.
Deviations that did not lead to discontinuation cannot be counted here, so no statement is made about their number or their effect on the primary endpoint.
