{{< include /_setup.qmd >}}

# Primary and secondary endpoints

## Primary endpoint: time to first dermatologic event

::: {#tbl-tte}

```{r}
#| label: tte

tlf_output(tlf_tte_summary(adtte), "tte")
```

`{r} tlf_caption("tte")`

:::

::: {#fig-km}

```{r}
#| label: km
#| fig-alt: "Kaplan-Meier cumulative incidence curves by treatment group, with confidence bands and a table of subjects at risk. Both xanomeline groups rise faster than placebo."
#| fig-height: 4.5

fig_km(adtte)
```

`{r} tlf_caption("km")`

:::

Both xanomeline groups reached a higher cumulative incidence of dermatologic events than placebo, and the separation appeared within the first weeks of treatment.
The hazard ratios in @tbl-tte quantify that difference; the confidence intervals exclude one for both dose groups.

`r counts[["censored_before_first_dose"]]` subjects have a last date known to be alive that precedes their first dose in the source data, and are censored at day 1 rather than excluded, which is the behaviour of `admiral::derive_param_tte()`.
They enter the risk set for the first day only, so their influence on the estimates is negligible without being nil.

### Supportive analysis: per-protocol population

::: {#tbl-tte-pp}

```{r}
#| label: tte-pp

tlf_output(tlf_tte_summary(dplyr::filter(adtte, PPROTFL == "Y")), "tte_pp")
```

`{r} tlf_caption("tte_pp")`

:::

The per-protocol result in @tbl-tte-pp is consistent in direction and magnitude with the intention-to-treat result in @tbl-tte, supporting the primary conclusion.

### Subgroup analysis

::: {#fig-forest}

```{r}
#| label: forest
#| fig-alt: "Forest plot of hazard ratios and 95% confidence intervals for xanomeline (any dose) versus placebo, shown overall and within sex and age-group subgroups. All point estimates fall to the right of the line of no effect."
#| fig-height: 4

fig_forest_subgroup(adtte)
```

`{r} tlf_caption("forest")`

:::

The treatment effect on the primary endpoint was consistent across sex and age-group subgroups, with no confidence interval crossing the line of no effect.

## Secondary endpoint: change in systolic blood pressure

::: {#tbl-ancova}

```{r}
#| label: ancova

tlf_output(tlf_vitals_ancova(advs), "ancova")
```

`{r} tlf_caption("ancova")`

:::

::: {#fig-vitals-profile}

```{r}
#| label: vitals
#| fig-alt: "Line chart of mean systolic blood pressure by scheduled visit for each treatment group, with error bars showing the standard error."
#| fig-height: 4

fig_vitals_profile(advs)
```

`{r} tlf_caption("vitals_profile")`

:::

Mean systolic blood pressure remained stable across the treatment period in all three groups.
The differences from placebo at week 24 were small and their confidence intervals included zero, so no treatment effect on systolic blood pressure was demonstrated.
