{{< include /_setup.qmd >}}

# Primary and secondary endpoints

## Primary endpoint: time to first dermatologic event

```{r}
#| label: tte

tlf_tte_summary(adtte) |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Table 14.2.1: Time to first dermatologic treatment-emergent adverse event"),
    subtitle = gt::md("Safety population")
  ) |>
  gt::tab_source_note(
    gt::md("Medians and confidence intervals are Kaplan-Meier estimates. Hazard ratios come from a Cox proportional hazards model with treatment as the only covariate and placebo as the reference group.")
  )
```

```{r}
#| label: km
#| fig-cap: "Figure 14.2.1: Cumulative incidence of the first dermatologic treatment-emergent adverse event, safety population."
#| fig-alt: "Kaplan-Meier cumulative incidence curves by treatment group, with confidence bands and a table of subjects at risk. Both xanomeline groups rise faster than placebo."
#| fig-height: 4.5

fig_km(adtte)
```

Both xanomeline groups reached a higher cumulative incidence of dermatologic events than placebo, and the separation appeared within the first weeks of treatment.
The hazard ratios in Table 14.2.1 quantify that difference; the confidence intervals exclude one for both dose groups.

### Supportive analysis: per-protocol population

```{r}
#| label: tte-pp

adtte |>
  dplyr::filter(PPROTFL == "Y") |>
  tlf_tte_summary() |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Table 14.2.1.1: Time to first dermatologic treatment-emergent adverse event (supportive analysis)"),
    subtitle = gt::md("Per-protocol population")
  ) |>
  gt::tab_source_note(
    gt::md("Medians and confidence intervals are Kaplan-Meier estimates. Hazard ratios come from a Cox proportional hazards model with treatment as the only covariate and placebo as the reference group. The per-protocol population is restricted to safety-population subjects who completed the study.")
  )
```

The per-protocol result in Table 14.2.1.1 is consistent in direction and magnitude with the intention-to-treat result in Table 14.2.1, supporting the primary conclusion.

### Subgroup analysis

```{r}
#| label: forest
#| fig-cap: "Figure 14.2.3: Hazard ratio for the primary endpoint by age group and sex, safety population."
#| fig-alt: "Forest plot of hazard ratios and 95% confidence intervals for xanomeline (any dose) versus placebo, shown overall and within sex and age-group subgroups. All point estimates fall to the right of the line of no effect."
#| fig-height: 4

fig_forest_subgroup(adtte)
```

The treatment effect on the primary endpoint was consistent across sex and age-group subgroups, with no confidence interval crossing the line of no effect.

## Secondary endpoint: change in systolic blood pressure

```{r}
#| label: ancova

tlf_vitals_ancova(advs) |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Table 14.2.2: Change from baseline in systolic blood pressure at week 24"),
    subtitle = gt::md("Safety population")
  ) |>
  gt::tab_source_note(
    gt::md("Least-squares means from an analysis of covariance model with treatment group as a factor and the baseline value as a covariate.")
  )
```

```{r}
#| label: vitals
#| fig-cap: "Figure 14.2.2: Mean systolic blood pressure by visit and treatment group, safety population."
#| fig-alt: "Line chart of mean systolic blood pressure by scheduled visit for each treatment group, with error bars showing the standard error."
#| fig-height: 4

fig_vitals_profile(advs)
```

Mean systolic blood pressure remained stable across the treatment period in all three groups.
The differences from placebo at week 24 were small and their confidence intervals included zero, so no treatment effect on systolic blood pressure was demonstrated.
