{{< include /_setup.qmd >}}

# Safety evaluation

## Extent of exposure

```{r}
#| label: exposure

tlf_exposure(adex) |>
  tbl_nordvale(
    title = "Table 14.3.1: Extent of exposure",
    subtitle = "Safety population",
    source_note = "Exposure is the total treatment duration in days, derived from the exposure analysis dataset."
  )
```

## Overview of adverse events

```{r}
#| label: ae-overview

tlf_ae_overview(adae, adsl) |>
  tbl_nordvale(
    title = "Table 14.3.2: Overview of treatment-emergent adverse events",
    subtitle = "Safety population",
    source_note = "Subjects are counted once in each row. A treatment-emergent adverse event started on or after the first dose of study drug."
  )
```

## Adverse events by system organ class and preferred term

```{r}
#| label: ae-soc-pt

tlf_ae_by_soc_pt(adae, adsl) |>
  tbl_nordvale(
    title = "Table 14.3.3: Treatment-emergent adverse events by system organ class and preferred term",
    subtitle = "Events reported by at least 5% of subjects, safety population",
    source_note = "Subjects reporting more than one event within a system organ class or preferred term are counted once."
  )
```

Application-site and other dermatologic events dominated the adverse event profile in both xanomeline groups.
The pattern is consistent with the transdermal delivery system and with the primary endpoint result in Table 14.2.1.

## Adverse events by maximum severity

```{r}
#| label: ae-severity

tlf_ae_by_severity(adae, adsl) |>
  tbl_nordvale(
    title = "Table 14.3.4: Treatment-emergent adverse events by maximum severity",
    subtitle = "Events reported by at least 5% of subjects, safety population",
    source_note = "Subjects reporting more than one event within a preferred term are counted once, under the highest severity reported for that term."
  )
```

## Adverse events by relationship to study drug

```{r}
#| label: ae-relationship

tlf_ae_by_relationship(adae, adsl) |>
  tbl_nordvale(
    title = "Table 14.3.5: Treatment-emergent adverse events by relationship to study drug",
    subtitle = "Events reported by at least 5% of subjects, safety population",
    source_note = "Subjects reporting more than one event within a preferred term are counted once, as related if any event for that term was investigator-assessed as related."
  )
```

## Serious adverse events and deaths

```{r}
#| label: ae-serious

tlf_ae_serious(adae, adsl) |>
  tbl_nordvale(
    title = "Table 14.3.6: Serious treatment-emergent adverse events",
    subtitle = "Safety population",
    source_note = "Seriousness was assessed by the investigator according to the protocol definition."
  )
```

Subject-level detail for every serious event is listed in @sec-appendix-tlf.

## Laboratory evaluations

```{r}
#| label: lab-shift
#| output: asis

lab_shift_panel <- c(
  "Alanine Aminotransferase (U/L)" = "Alanine aminotransferase",
  "Aspartate Aminotransferase (U/L)" = "Aspartate aminotransferase",
  "Bilirubin (umol/L)" = "Bilirubin",
  "Creatinine (umol/L)" = "Creatinine"
)

tlf_shift_panel(adlb, lab_shift_panel)
```

Shifts to a high category were infrequent for each analyte in this panel and distributed similarly across treatment groups.
No subject met the biochemical criteria for a drug-induced liver injury.

## Vital signs

```{r}
#| label: vitals-shift

tlf_shift(advs, "Systolic Blood Pressure (mmHg)") |>
  tbl_nordvale(
    title = "Table 14.3.8: Shift from baseline to worst post-baseline category",
    subtitle = "Systolic blood pressure, safety population",
    source_note = "Categories are relative to the reference range of the reporting site. The worst post-baseline category is high (hypertensive) if any post-baseline value was high, otherwise low (hypotensive) if any value was low."
  )
```

Shifts to a high systolic blood pressure category occurred at a similar rate across treatment groups, with no excess of new hypotensive or hypertensive categories in either xanomeline group relative to placebo.
