{{< include /_setup.qmd >}}

# Safety evaluation

Safety analyses count subjects under the treatment actually received, so the group sizes below differ from the randomised group sizes in the study patients chapter for the subjects whose actual treatment differed from their planned treatment.

## Extent of exposure

::: {#tbl-exposure}

```{r}
#| label: exposure

tlf_output(tlf_exposure(adex), "exposure")
```

`{r} tlf_caption("exposure")`

:::

## Prior and concomitant medications

::: {#tbl-conmeds}

```{r}
#| label: conmeds

tlf_output(tlf_conmeds(adcm, adsl), "conmeds")
```

`{r} tlf_caption("conmeds")`

:::

Concomitant medication use was extensive and comparable across the treatment groups, as expected in an elderly population.

## Overview of adverse events

::: {#tbl-ae-overview}

```{r}
#| label: ae-overview

tlf_output(tlf_ae_overview(adae, adsl), "ae_overview")
```

`{r} tlf_caption("ae_overview")`

:::

## Adverse events by system organ class and preferred term

::: {#tbl-ae-soc-pt}

```{r}
#| label: ae-soc-pt

tlf_output(tlf_ae_by_soc_pt(adae, adsl), "ae_soc_pt")
```

`{r} tlf_caption("ae_soc_pt")`

:::

Application-site and other dermatologic events dominated the adverse event profile in both xanomeline groups.
The pattern is consistent with the transdermal delivery system and with the primary endpoint result in @tbl-tte.

## Adverse events by maximum severity

::: {#tbl-ae-severity}

```{r}
#| label: ae-severity

tlf_output(tlf_ae_by_severity(adae, adsl), "ae_severity")
```

`{r} tlf_caption("ae_severity")`

:::

## Adverse events by relationship to study drug

::: {#tbl-ae-relationship}

```{r}
#| label: ae-relationship

tlf_output(tlf_ae_by_relationship(adae, adsl), "ae_relationship")
```

`{r} tlf_caption("ae_relationship")`

:::

## Serious adverse events and deaths

::: {#tbl-ae-serious}

```{r}
#| label: ae-serious

tlf_output(tlf_ae_serious(adae, adsl), "ae_serious")
```

`{r} tlf_caption("ae_serious")`

:::

Subject-level detail for every serious event is listed in @lst-sae.

### Narratives

ICH E3 requires a narrative for every death, every other serious adverse event, and any other adverse event judged to be of special interest.
Narratives are written from the source documents rather than from the analysis datasets, so they cannot be generated from the data in this demonstration.
One narrative is reproduced below to show the structure; the remainder would follow the same shape, one per event.

::: {.callout-note appearance="simple"}

**Subject 01-701-XXXX, placebo, serious adverse event.**
A subject in the placebo group experienced a serious adverse event during the treatment period.
The event began on the study day recorded in @lst-sae, was assessed by the investigator as not related to study drug, and resolved.
Study drug was not withdrawn and the subject continued in the study.

The subject identifier and the clinical content of this narrative are placeholders and are not drawn from the source data.

:::

## Laboratory evaluations

```{r}
#| label: lab-shift
#| output: asis

lab_shift_panel <- c(
  "Alanine Aminotransferase (U/L)" = "lab_shift_alt",
  "Aspartate Aminotransferase (U/L)" = "lab_shift_ast",
  "Bilirubin (umol/L)" = "lab_shift_bili",
  "Creatinine (umol/L)" = "lab_shift_creat"
)

tlf_shift_panel(adlb, lab_shift_panel)
```

Shifts to a high category were infrequent for each analyte in this panel and distributed similarly across treatment groups.

::: {#tbl-hys-law}

```{r}
#| label: hys-law

tlf_output(tlf_hys_law(adlb, adsl), "hys_law")
```

`{r} tlf_caption("hys_law")`

:::

```{r}
#| label: hys-law-numbers

hys_flags <- hys_law_flags(adlb)
hys_combined <- dplyr::filter(hys_flags, (alt_3x | ast_3x) & bili_2x)
hys_groups <- sort(unique(as.character(hys_combined[["TRTA"]])))
hys_any <- sum(hys_flags[["alt_3x"]] | hys_flags[["ast_3x"]] | hys_flags[["bili_2x"]])
```

Subjects meeting the combined aminotransferase and bilirubin criterion: `r nrow(hys_combined)`, in the following treatment groups: `r if (length(hys_groups) == 0L) "none" else paste(tolower(hys_groups), collapse = ", ")`.
`r hys_any` subjects met at least one criterion in total, too few for the difference between treatment groups to be interpretable, so the laboratory data show no signal of xanomeline-related liver injury.
Subject-level values for every subject meeting any criterion are listed in @lst-lab-abnormal.

## Vital signs

::: {#tbl-vitals-shift}

```{r}
#| label: vitals-shift

tlf_output(
  tlf_shift(advs, "Systolic Blood Pressure (mmHg)", basetype = vitals_basetype),
  "vitals_shift"
)
```

`{r} tlf_caption("vitals_shift")`

:::

Shifts to a high systolic blood pressure category occurred at a similar rate across treatment groups, with no excess of new hypotensive or hypertensive categories in either xanomeline group relative to placebo.

## Electrocardiogram

::: {#tbl-ecg-shift}

```{r}
#| label: ecg-shift

tlf_output(tlf_ecg_shift(adeg), "ecg_shift")
```

`{r} tlf_caption("ecg_shift")`

:::

The QTcF interval is the only electrocardiogram parameter carrying reference-range indicators in these data.
Shifts out of the normal range were infrequent and showed no dose-related pattern.
