{{< include /_setup.qmd >}}

# Reproducibility {#sec-reproducibility}

## Source data

The analysis datasets are the CDISC pilot study datasets (study identifier `CDISCPILOT01`) distributed in the `pharmaverseadam` package.
`R/00-adam.R` reads those datasets, restricts them to the randomised treatment groups, derives the treatment-emergent flags used throughout the report, and derives the time-to-event dataset with `admiral::derive_param_tte()`.

## Metadata excerpt (define.xml style)

A define.xml documents every submitted dataset and variable: its name, label, data type and, where applicable, the controlled terminology codelist it draws from.
Tools such as `metacore` build a validated metadata object from that specification; the excerpt below hand-curates a subset of ADSL variables used in this report in the same shape, without generating or validating a full define.xml.

```{r}
#| label: define-excerpt

tibble::tribble(
  ~Dataset, ~Variable, ~Label, ~Type, ~Codelist,
  "ADSL", "USUBJID", "Unique Subject Identifier", "text", "",
  "ADSL", "TRT01P", "Planned Treatment for Period 01", "text", "TRT01P",
  "ADSL", "TRT01A", "Actual Treatment for Period 01", "text", "TRT01P",
  "ADSL", "AGE", "Age", "integer", "",
  "ADSL", "AGEGR1", "Pooled Age Group 1", "text", "AGEGR1",
  "ADSL", "SEX", "Sex", "text", "SEX",
  "ADSL", "RACE", "Race", "text", "RACE",
  "ADSL", "SAFFL", "Safety Population Flag", "text", "NY",
  "ADSL", "ITTFL", "Intent-To-Treat Population Flag", "text", "NY",
  "ADSL", "PPROTFL", "Per-Protocol Population Flag", "text", "NY",
  "ADSL", "COMPFL", "Completers Population Flag", "text", "NY",
  "ADSL", "TRTDURD", "Total Treatment Duration (Days)", "integer", ""
) |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Metadata excerpt: ADSL variables used in this report"),
    subtitle = gt::md("define.xml-style excerpt, hand-curated")
  ) |>
  gt::tab_source_note(
    gt::md("Illustrative excerpt only, covering the ADSL variables referenced elsewhere in this report; not a validated define.xml. `NY` is the CDISC controlled terminology codelist for No/Yes flags.")
  )
```

## Analysis results traceability

Every summary table in this report is computed by `gtsummary`, which retains the Analysis Results Dataset (ARD) behind each statistic, following the CDISC Analysis Results Data standard.
Each table's ARD can be recovered from its table object, and `cards::bind_ard()` combines the ARDs from several tables into a single dataset, which is the mechanism used for quality control of the numbers reported here.

```{r}
#| label: ard-example
#| echo: true

disposition_ard <- gtsummary::gather_ard(tlf_disposition(adsl))[[1L]]
demographics_ard <- gtsummary::gather_ard(tlf_demographics(adsl))[[1L]]
ae_overview_ard <- gtsummary::gather_ard(tlf_ae_overview(adae, adsl))[[1L]]

ard <- cards::bind_ard(disposition_ard, demographics_ard, ae_overview_ard, .quiet = TRUE)
head(as.data.frame(ard)[, c("variable", "stat_name", "stat")], 8)
```

The combined ARD traces every statistic back to the table (Table 14.1.1, Table 14.1.2 or Table 14.3.2) and variable that produced it:

```{r}
#| label: ard-by-variable
#| echo: true

as.data.frame(dplyr::count(ard, variable, name = "n_rows"))
```

## Session information

```{r}
#| label: session-info

sessioninfo::session_info(pkgs = "attached")$packages |>
  as.data.frame() |>
  dplyr::filter(package %in% c(
    "admiral", "cards", "cardx", "dplyr", "ggplot2", "ggsurvfit",
    "gt", "gtsummary", "pharmaverseadam", "survival"
  )) |>
  dplyr::transmute(
    Package = package,
    Version = loadedversion,
    Source = source
  ) |>
  gt_nordvale() |>
  gt::tab_header(title = gt::md("Package versions used for this report"))
```

Key packages are cited in the reference list: admiral [@admiral], gtsummary [@gtsummary], survival [@survival], ggsurvfit [@ggsurvfit], gt [@gt].

## Table shells

Table shells fix column layout, statistics and placeholder text at SAP sign-off, before database lock.
The final report differs from the shell only in the numbers, not in structure.
The mockup below is the pre-lock shell for Table 14.2.1; the populated table that follows is the same table after database lock, reproduced here for direct comparison (it also appears as Table 14.2.1 in the primary and secondary endpoints chapter).

```{r}
#| label: shell-tte

tibble::tibble(
  `Treatment group` = c("Placebo", "Xanomeline low dose", "Xanomeline high dose"),
  `Subjects` = c("XX", "XX", "XX"),
  `Subjects with an event` = c("XX (XX.X%)", "XX (XX.X%)", "XX (XX.X%)"),
  `Median time to event (days)` = c("XXX (XXX, XXX)", "XXX (XXX, XXX)", "XXX (XXX, XXX)"),
  `Hazard ratio (95% CI)` = c("Reference", "X.XX (X.XX, X.XX)", "X.XX (X.XX, X.XX)"),
  `p-value` = c("", "X.XXX", "X.XXX")
) |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Table 14.2.1 (shell): Time to first dermatologic treatment-emergent adverse event"),
    subtitle = gt::md("Safety population &mdash; pre-database-lock template")
  ) |>
  gt::tab_source_note(
    gt::md("`XX` marks cells populated only after database lock. Column layout and statistics are fixed at SAP sign-off.")
  )
```

```{r}
#| label: shell-tte-final

tlf_tte_summary(adtte) |>
  gt_nordvale() |>
  gt::tab_header(
    title = gt::md("Table 14.2.1: Time to first dermatologic treatment-emergent adverse event"),
    subtitle = gt::md("Safety population")
  ) |>
  gt::tab_source_note(
    gt::md("Medians and confidence intervals are Kaplan-Meier estimates. Hazard ratios come from a Cox proportional hazards model with treatment as the only covariate and placebo as the reference group.")
  )
```

```{r}
#| label: quarto-version
#| echo: true

quarto_version <- system2("quarto", "--version", stdout = TRUE, stderr = TRUE)
typst_version <- system2("quarto", c("typst", "--version"), stdout = TRUE, stderr = TRUE)

cat(
  "R:     ", R.version.string,
  "\nQuarto:", quarto_version,
  "\nTypst: ", sub("^typst ", "", typst_version)
)
```

The exact package versions are pinned in `renv.lock`.
Running `renv::restore()` followed by `quarto render` reproduces this report from a clean checkout.
