{{< include /_setup.qmd >}}

# Listings {#sec-appendix-tlf}

<!-- Quarto left-aligns listing floats for code listings and injects that show
rule before the body, so it beats anything the format template sets. These
listings are tabular subject data, so they follow the tables and stay centred. -->

```{=typst}
#show figure.where(kind: "quarto-float-lst"): set align(center)
```

## Individual subject data listings

::: {.landscape}

::: {#lst-discontinuation}

```{r}
#| label: listing-discontinuation

tlf_output(listing_discontinuation(adsl), "listing_discontinuation")
```

`{r} tlf_caption("listing_discontinuation")`

:::

::: {#lst-deviation}

```{r}
#| label: listing-deviation

tlf_output(listing_deviation(adsl), "listing_deviation")
```

`{r} tlf_caption("listing_deviation")`

:::

::: {#lst-demographics}

```{r}
#| label: listing-demographics

tlf_output(listing_demographics(adsl), "listing_demographics")
```

`{r} tlf_caption("listing_demographics")`

:::

::: {#lst-sae}

```{r}
#| label: listing-sae

tlf_output(listing_serious_ae(adae), "listing_sae")
```

`{r} tlf_caption("listing_sae")`

:::

::: {#lst-lab-abnormal}

```{r}
#| label: listing-lab-abnormal

tlf_output(listing_lab_abnormal(adlb), "listing_lab_abnormal")
```

`{r} tlf_caption("listing_lab_abnormal")`

:::

:::

## Index of outputs

Quarto numbers the tables, figures and listings of this report in the order they appear.
The index below maps each of those numbers to the ICH E3 output number it stands for, and to the ICH E3 section that number belongs to.

```{r}
#| label: tlf-catalogue
#| output: asis

tlf_catalogue()
```
