{{< include /_setup.qmd >}}

# Listings {#sec-appendix-tlf}

<!-- Quarto left-aligns listing floats for code listings and injects that show
rule before the body, so it beats anything the format template sets. These
listings are tabular subject data, so they follow the tables and stay centred. -->

```{=typst}
#show figure.where(kind: "quarto-float-lst"): set align(center)
```

## Individual subject data listings

::: {#lst-discontinuation}

```{r}
#| label: listing-discontinuation

tlf_output(listing_discontinuation(adsl), "listing_discontinuation")
```

`{r} tlf_caption("listing_discontinuation")`

:::

::: {#lst-deviation}

```{r}
#| label: listing-deviation

tlf_output(listing_deviation(adsl), "listing_deviation")
```

`{r} tlf_caption("listing_deviation")`

:::

::: {#lst-demographics}

```{r}
#| label: listing-demographics

tlf_output(listing_demographics(adsl), "listing_demographics")
```

`{r} tlf_caption("listing_demographics")`

:::

::: {.landscape}

::: {#lst-sae}

```{r}
#| label: listing-sae

tlf_output(listing_serious_ae(adae), "listing_sae")
```

`{r} tlf_caption("listing_sae")`

:::

::: {#lst-lab-abnormal}

```{r}
#| label: listing-lab-abnormal

tlf_output(listing_lab_abnormal(adlb), "listing_lab_abnormal")
```

`{r} tlf_caption("listing_lab_abnormal")`

:::

:::

## Index of outputs

Every table, figure and listing of this report carries the ICH E3 output number that `R/tlf-index.R` holds for it.
The index below lists them all, with the ICH E3 section each number belongs to and the population the output was computed on.

```{r}
#| label: tlf-catalogue
#| output: asis

tlf_catalogue()
```
