{{< include /_setup.qmd >}}

# Listings {#sec-appendix-tlf}

## Individual subject data listings

::: {#listing-discontinuation}

```{r}
#| label: listing-discontinuation

tlf_output(listing_discontinuation(adsl), "listing_discontinuation")
```

`{r} tlf_caption("listing_discontinuation")`

:::

::: {#listing-deviation}

```{r}
#| label: listing-deviation

tlf_output(listing_deviation(adsl), "listing_deviation")
```

`{r} tlf_caption("listing_deviation")`

:::

::: {#listing-demographics}

```{r}
#| label: listing-demographics

tlf_output(listing_demographics(adsl), "listing_demographics")
```

`{r} tlf_caption("listing_demographics")`

:::

::: {.landscape}

::: {#listing-sae}

```{r}
#| label: listing-sae

tlf_output(listing_serious_ae(adae), "listing_sae")
```

`{r} tlf_caption("listing_sae")`

:::

::: {#listing-lab-abnormal}

```{r}
#| label: listing-lab-abnormal

tlf_output(listing_lab_abnormal(adlb), "listing_lab_abnormal")
```

`{r} tlf_caption("listing_lab_abnormal")`

:::

:::

## Index of outputs

Every table, figure and listing of this report carries the ICH E3 output number that `R/tlf-index.R` holds for it.
The index below lists them all, with the ICH E3 section each number belongs to and the population the output was computed on.

```{r}
#| label: tlf-catalogue
#| output: asis

tlf_catalogue()
```
